Models pretest

### 2022-12-07 Submission/Models_pretest.Rmd
one more model

---
title: "Models pretest"
author: "Henrique Sposito and Livio Silva-Muller"
date: "2022-12-06"
output:
  pdf_document: default
  html_document: default
  fig_caption: yes
---

@@

>>>>

---
title: "Models pretest"
author: "Henrique Sposito and Livio Silva-Muller"
date: "2022-12-06"
output:
  html_document: default
  pdf_document: default
  fig_caption: yes
---

@@

```{r models president fixed effect, fig.cap="Logistic Regressions Output with President fixed effecr", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

model_logit_con_pfe <- plm(con_vs_all ~ as.factor(location_cat) + 
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
model_logit_ei_pfe <- plm(EI_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
model_logit_sd_pfe <- plm(SD_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
model_logit_sov_pfe <- plm(sov_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
model_logit_all_pfe <- plm(amazon_speech ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model2_lag,
                         model = "within", index = "president")

stargazer::stargazer(model_logit_con_pfe, model_logit_ei_pfe, model_logit_sd_pfe,
                     model_logit_sov_pfe, model_logit_all_pfe, digits = 6,
                     no.space = TRUE,
                     title = "Logistic Regressions with president fixed-effects")
